Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-29 MDPI_submission.Rmd
Commit 2023-11-29 21:09

LT$cor.df           <- NULL
LT$cor.null_value   <- NULL
LT$cor.alternative  <- NULL
LT$cor.method       <- NULL
LT$cor.data_name    <- NULL
LT$cor.p            <- NULL

names(LT)    <- c("Trend [%/year]",
                  "Trend p-value",
                  "Sky conditions",
                  "Days with data",
                  "Statistical signif. [%]")
## no need all are 100%
LTminSSig <- signif(min(LT$`Statistical signif. [%]`), 4)
# LT$`Trend statistical signif. [%]` <- NULL
## numeric precision
LT$`Trend [%/year]` <- signif(LT$`Trend [%/year]`, 3)
LT$`Trend p-value`  <- signif(LT$`Trend p-value`,  3)

## some vars to use later
alltrend   <- signif(LT[`Sky conditions` == "All sky cond.",    `Trend [%/year]`], 2)
cleartrend <- signif(LT[`Sky conditions` == "Clear sky cond.",  `Trend [%/year]`], 2)
cloudtrend <- signif(LT[`Sky conditions` == "Cloudy sky cond.", `Trend [%/year]`], 2)
## rename sky conditions
LT$`Sky conditions` <- sub(" cond.", "", LT$`Sky conditions`)

## order columns
LT1 <- LT[,c(
      "Sky conditions",
      "Trend [%/year]",
      "Trend p-value",
      "Days with data"
      )]

## order columns
LT2 <- LT[,c(
      "Sky conditions",
      "Trend [%/year]",
      "Statistical signif. [%]",
      "Days with data"
      )]
```

@@

```{r echo=F, eval=TRUE}
## Prepare table and data
spp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep         = ";",
               header      = TRUE)
spp <- spp[grep("SDR" ,spp$var), ]
spp$slope.sd           <- NULL
spp$slope.ConfInt_0.95 <- NULL
spp$slope.ConfInt_0.99 <- NULL
spp$var                <- NULL
rownames(spp)          <- NULL
names(spp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x, spp){which(spp$Season == x)}, spp = spp)
spp        <- spp[new_order,]
## order by sky condition
spp <- spp[order(spp$`Sky condition`),]

# ## put all sky first
# A  <- which(spp$`Sky condition` == "All sky cond.")
# B  <- which(spp$`Sky condition` != "All sky cond.")
# spp <- spp[c(A,B),]
## numeric precision
spp$`Trend [%/year]`          <- signif(spp$`Trend [%/year]`, 3)
spp$`Trend p-value`           <- signif(spp$`Trend p-value`,  3)
spp$`Statistical signif. [%]` <- signif(spp$`Statistical signif. [%]`,  3)

## rename sky conditions
spp$`Sky condition` <- sub(" cond.", "", spp$`Sky condition`)
```

@@

```{r trendseasontable, echo=F}
## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]",
      # "Trend p-value",
      "Statistical signif. [%]"
      )]
spp2 <- spp
## rename conditions
spp2$`Sky condition` <- sub(" sky", " skies", spp2$`Sky condition`)

>>>>

LT$cor.df           <- NULL
LT$cor.null_value   <- NULL
LT$cor.alternative  <- NULL
LT$cor.method       <- NULL
LT$cor.data_name    <- NULL
LT$cor.p            <- NULL
LT$conf.level       <- NULL

## some vars to use later
alltrend   <- signif(LT[DATA == "All sky cond.",    slope], 2)
cleartrend <- signif(LT[DATA == "Clear sky cond.",  slope], 2)
cloudtrend <- signif(LT[DATA == "Cloudy sky cond.", slope], 2)
LTminSSig  <- signif(min(LT$slope.stat_sig), 4)

## numeric precision of table
LT$slope    <- signif(LT$slope,   3)
LT$slope.p  <- signif(LT$slope.p, 3)
## rename sky conditions
LT$DATA <- sub(" cond.", "", LT$DATA)

# 
# names(LT)    <- c("Trend [%/year]",
#                   "Trend p-value",
#                   "Sky conditions",
#                   "Days with data",
#                   "Statistical signif. [%]")

## no need all are 100%

# LT$`Trend statistical signif. [%]` <- NULL

## order columns
# LT1 <- LT[,c(
#       "Sky conditions",
#       "Trend [%/year]",
#       "Trend p-value",
#       "Days with data"
#       )]

## order columns
# LT2 <- LT[,c(
#       "Sky conditions",
#       "Trend [%/year]",
#       "Statistical signif. [%]",
#       "Days with data"
#       )]
LT2 <- LT
```

@@

```{r echo=F, eval=TRUE}
## Prepare table and data
spp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep         = ";",
               header      = TRUE)
spp <- spp[grep("SDR" ,spp$var), ]
spp$slope.sd           <- NULL
spp$slope.ConfInt_0.95 <- NULL
spp$slope.ConfInt_0.99 <- NULL
spp$var                <- NULL

spp$cor.df             <- NULL
spp$cor.null_value     <- NULL
spp$cor.alternative    <- NULL
spp$cor.method         <- NULL
spp$cor.data_name      <- NULL
spp$cor.p              <- NULL
spp$conf.level         <- NULL

rownames(spp)          <- NULL

## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x, spp){which(spp$Season == x)}, spp = spp)
spp       <- spp[new_order,]
## order by sky condition
spp <- spp[order(spp$DATA), ]

## numeric precision
spp$slope          <- signif(spp$slope,          3)
spp$slope.p        <- signif(spp$slope.p,        3)
spp$slope.stat_sig <- signif(spp$slope.stat_sig, 3)

## rename sky conditions
spp$DATA <- sub(" cond.", "", spp$DATA)
## rename conditions
spp$DATA <- sub(" sky", " skies", spp$DATA)

# names(spp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")

# ## put all sky first
# A  <- which(spp$`Sky condition` == "All sky cond.")
# B  <- which(spp$`Sky condition` != "All sky cond.")
# spp <- spp[c(A,B),]

```

@@

```{r trendseasontable, echo=F}
## arrange columns
# spp <- spp[,c(
#       "Sky condition",
#       "Season",
#       "Trend [%/year]",
#       # "Trend p-value",
#       "Statistical signif. [%]"
#       )]

spp2 <- spp
